Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics

### 2020-01-12 paper/paper.Rmd
doone with design, need to look at null gen next

## Variables

The variables changed between groups were the type of plot shown and the trend model.

A combination of map type and spatial trend model created the twenty-four lineup displays. We split this set of displays into a collection of twelve displays for Group A and twelve displays for Group B. 
The random allocation of participants to Group A or Group B resulted in 42 participants allocated to Group A and 53 participants allocated to Group B.

The levels of the factors measured in the experiment were:

  - Map type: *Choropleth, Hexagon tile*
  - Trend: *Locations in three population centres, Locations in multiple population centres, South-East to North-West*

Each group did not see the same data for both map types. We generated four simulated sets of data for each treatment.
This will generate twenty-four lineups (twelve lineups of geographic maps and twelve lineups of hexagon tile maps). Participants evaluated twelve lineups, size of each map type.
For each of the six geographic displays and six hexagon displays, two of each trend model were shown to the participants. We outline the design in Table. \ref{tab:exp-design}.

@@

The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
To measure the accuracy of the detections, the plot chosen for each lineup evaluated was compared to the position of the real spatial trend plot in the lineup. A correct result occurs when the chosen plot matches the position of the real plot, this was recorded in an additional binary variable; 1 = correct; 0 = incorrect.
High efficiency occurs when a small amount of time is taken to evaluate each lineup. This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.

## Simulation process

>>>>

## Experimental factors

<!-- The variables changed between groups were the type of plot shown and the trend model.-->

The primary factor in the experiment is the plot type. The secondary factor is a trend model. Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing level of inner city hot spots. These latter two reflect the structure seen in the liver cancer data (Figure \ref{fig:liver}). This produces six treatment levels:

  - Map type: *Choropleth, Hexagon tile*
  - Trend: *South-East to North-West; Locations in three population centres; Locations in multiple population centres, *

Data is generated for each of the trend models, with four replicates, and each displayed both as a choropleth and as a hexagon tile map, which yields 12 data sets, and 24 data plots. This set of displays is divided in half, providing two sets of 12 displays, Group A and Group B. Participants were randomly allocated to Group A or B. Participants saw a data set only once, with as a choropleth or as a hexagon tile map. Table \ref{tab:exp-design} summarise the design. (XXX Maybe replace this table with your diagram illustrating the design??)

<!-- Each group did not see the same data for both map types. We generated four simulated sets of data for each treatment.
This will generate twenty-four lineups (twelve lineups of geographic maps and twelve lineups of hexagon tile maps). Participants evaluated twelve lineups, size of each map type.
For each of the six geographic displays and six hexagon displays, two of each trend model were shown to the participants. We outline the design in Table \ref{tab:exp-design}.
-->

@@

<!-- The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
To measure the accuracy of the detections, the plot chosen for each lineup evaluated was compared to the position of the real spatial trend plot in the lineup. A correct result occurs when the chosen plot matches the position of the real plot, this was recorded in an additional binary variable; 1 = correct; 0 = incorrect.
High efficiency occurs when a small amount of time is taken to evaluate each lineup. This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.-->

## Generating null data

### 2020-01-12 paper/paper.tex
doone with design, need to look at null gen next

\hypertarget{variables}{%
\subsection{Variables}\label{variables}}

The variables changed between groups were the type of plot shown and the trend model.

A combination of map type and spatial trend model created the twenty-four lineup displays. We split this set of displays into a collection of twelve displays for Group A and twelve displays for Group B.
The random allocation of participants to Group A or Group B resulted in 42 participants allocated to Group A and 53 participants allocated to Group B.

The levels of the factors measured in the experiment were:

\begin{itemize}
\tightlist
\item
  Map type: \emph{Choropleth, Hexagon tile}
\item
  Trend: \emph{Locations in three population centres, Locations in multiple population centres, South-East to North-West}
\end{itemize}

Each group did not see the same data for both map types. We generated four simulated sets of data for each treatment.
This will generate twenty-four lineups (twelve lineups of geographic maps and twelve lineups of hexagon tile maps). Participants evaluated twelve lineups, size of each map type.
For each of the six geographic displays and six hexagon displays, two of each trend model were shown to the participants. We outline the design in Table. \ref{tab:exp-design}.

@@

The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
To measure the accuracy of the detections, the plot chosen for each lineup evaluated was compared to the position of the real spatial trend plot in the lineup. A correct result occurs when the chosen plot matches the position of the real plot, this was recorded in an additional binary variable; 1 = correct; 0 = incorrect.
High efficiency occurs when a small amount of time is taken to evaluate each lineup. This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.

\hypertarget{simulation-process}{%
\subsection{Simulation process}\label{simulation-process}}

>>>>

\hypertarget{experimental-factors}{%
\subsection{Experimental factors}\label{experimental-factors}}

The primary factor in the experiment is the plot type. The secondary factor is a trend model. Three trend models were developed, one mirroring a large spatial trend for which the choropleth would be expected to do well, and two with differing level of inner city hot spots. These latter two reflect the structure seen in the liver cancer data (Figure \ref{fig:liver}). This produces six treatment levels:

\begin{itemize}
\tightlist
\item
  Map type: \emph{Choropleth, Hexagon tile}
\item
  Trend: \emph{South-East to North-West; Locations in three population centres; Locations in multiple population centres, }
\end{itemize}

Data is generated for each of the trend models, with four replicates, and each displayed both as a choropleth and as a hexagon tile map, which yields 12 data sets, and 24 data plots. This set of displays is divided in half, providing two sets of 12 displays, Group A and Group B. Participants were randomly allocated to Group A or B. Participants saw a data set only once, with as a choropleth or as a hexagon tile map. Table \ref{tab:exp-design} summarise the design. (XXX Maybe replace this table with your diagram illustrating the design??)

@@

\hypertarget{generating-null-data}{%
\subsection{Generating null data}\label{generating-null-data}}
